---
title: "Extra Elements"
author: "David Granjon"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Extra Elements}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Accordion
Accordions are a category of collapsible elements. While collapsible items do not 
alter the state of other items in the same collapsible container, each accordion item will 
toggle any other opened accordion, to ensure that only 1 item is visible at once. `accordion()` 
expects to contain `accordionItems()`. Importantly, to guaranty the uniqueness of each accordion, 
we must provide an __id__ parameter. This parameter allows to programmatically toggle any accordion item, 
through an `updateAccordion()` function.

```{r accordion-code, eval=FALSE}
library(shiny)
library(bs4Dash)

 shinyApp(
  ui = dashboardPage(
    dashboardHeader(),
    dashboardSidebar(),
    dashboardBody(
      radioButtons("controller", "Controller", choices = c(1, 2)),
      br(),
      accordion(
       id = "accordion1",
        accordionItem(
          title = "Accordion 1 Item 1",
          status = "danger",
          collapsed = TRUE,
          "This is some text!"
        ),
        accordionItem(
          title = "Accordion 1 Item 2",
          status = "warning",
          collapsed = FALSE,
          "This is some text!"
        )
      ),
      accordion(
       id = "accordion2",
        accordionItem(
          title = "Accordion 2 Item 1",
          status = "info",
          collapsed = TRUE,
          "This is some text!"
        ),
        accordionItem(
          title = "Accordion 2 Item 2",
          status = "success",
          collapsed = FALSE,
          "This is some text!"
        )
      )
    ),
    title = "Accordion"
  ),
  server = function(input, output, session) {
    observeEvent(input$controller, {
      updateAccordion(id = "accordion1", selected = input$controller)
    })
    
    observe(print(input$accordion1))
    
    observeEvent(input$accordion1, {
      toast(sprintf("You selected accordion N° %s", input$accordion1))
    })
  }
 )
```

<div class="marvel-device ipad black">
<div class="camera"></div>
<div class="screen">
<iframe width="100%" src="https://dgranjon.shinyapps.io/bs4Dash-accordions/" allowfullscreen="" frameborder="0" scrolling="yes" height="770px"></iframe>
</div>
<div class="home"></div>
</div>


## User messages
`{bs4Dash}` make it possible to create an entire chat system within a Shiny app. `userMessages()` 
is the main container, `userMessage()` being the message element. `updateUserMessages()` 
looks for the `userMessages()` __id__ so as to:

- Remove an existing message.
- Add a new message.
- Edit an existing message.

Importantly, we assume that a message structure is composed as follows:

```{r message-code, eval=FALSE}
list(
  author = "David",
  date = "Now",
  image = "https://i.pinimg.com/originals/f1/15/df/f115dfc9cab063597b1221d015996b39.jpg",
  type = "received",
  text = tagList(
    sliderInput(
      "obs", 
      "Number of observations:",
      min = 0, 
      max = 1000, 
      value = 500
    ),
    plotOutput("distPlot")
  )
```

The __type__ parameter controls the message background color. For a sent message, 
the color is inherited from the `userMessages()` status, while for a received message, 
the color is gray by default. The __text__ argument refers to the message content. It may be simple text, 
shiny tags or event any combinations of shiny inputs/ouput, as shown in the below example.


```{r chat-code, eval=FALSE}
shinyApp(
  ui = dashboardPage(
    dashboardHeader(),
    dashboardSidebar(),
    dashboardBody(
      fluidRow(
        actionButton("remove", "Remove message"),
        actionButton("add", "Add message"),
        actionButton("update", "Update message")
      ),
      numericInput("index", "Message index:", 1, min = 1, max = 3),
      br(),
      br(),
      userMessages(
        width = 6,
        status = "danger",
        id = "message",
        userMessage(
          author = "Alexander Pierce",
          date = "20 Jan 2:00 pm",
          image = "https://adminlte.io/themes/AdminLTE/dist/img/user1-128x128.jpg",
          type = "received",
          "Is this template really for free? That's unbelievable!"
        ),
        userMessage(
          author = "Sarah Bullock",
          date = "23 Jan 2:05 pm",
          image = "https://adminlte.io/themes/AdminLTE/dist/img/user3-128x128.jpg",
          type = "sent",
          "You better believe it!"
        )
      )
    ),
    title = "user Message"
  ),
  server = function(input, output, session) {
    observeEvent(input$remove, {
      updateUserMessages("message", action = "remove", index = input$index)
    })
    observeEvent(input$add, {
      updateUserMessages(
        "message", 
        action = "add", 
        content = list(
          author = "David",
          date = "Now",
          image = "https://i.pinimg.com/originals/f1/15/df/f115dfc9cab063597b1221d015996b39.jpg",
          type = "received",
          text = tagList(
           sliderInput(
            "obs", 
            "Number of observations:",
            min = 0, 
            max = 1000, 
            value = 500
           ),
           plotOutput("distPlot")
          )
        )
      )
    })
    
    output$distPlot <- renderPlot({
     hist(rnorm(input$obs))
    })
    
    observeEvent(input$update, {
      updateUserMessages(
        "message", 
        action = "update", 
        index = input$index,
        content = list(
         text = tagList(
          appButton(
           inputId = "reload",
           label = "Click me!", 
           icon = icon("sync"), 
           dashboardBadge(1, color = "danger")
          )
         )
        )
      )
    })

    observeEvent(input$reload, {
      toast(title = "Yeah")
    })
  }
)
```

<div class="marvel-device ipad black">
<div class="camera"></div>
<div class="screen">
<iframe width="100%" src="https://dgranjon.shinyapps.io/bs4Dash-userMessages/" allowfullscreen="" frameborder="0" scrolling="yes" height="770px"></iframe>
</div>
<div class="home"></div>
</div>